Design, Implementation, and Evaluation of Open Power Quality

### 2020-06-24 02-intro.tex
wave form -> waveform.

{\em Cloud-native information architecture.} Second, our information architecture is "cloud native", which means that OPQ Boxes are not designed for stand-alone, autonomous use, unlike current commercially available power quality monitors. Instead, our hardware boxes and cloud-based services perform real-time, two-way communication over the Internet to determine what power quality data must be gathered and with what fidelity in order to most efficiently produce actionable information. Two-way communication between the OPQ Boxes and cloud services creates the ability to control individual OPQ Boxes based upon the global state of all OPQ Boxes in an OPQ sensor network. As a result, OPQ cloud services can obtain and analyze high fidelity wave form data only when desired, without the prohibitive network overhead of constantly communicating this data from boxes to the cloud. This enables OPQ installations to be simultaneously responsive and scalable.

>>>>

{\em Cloud-native information architecture.} Second, our information architecture is "cloud native", which means that OPQ Boxes are not designed for stand-alone, autonomous use, unlike current commercially available power quality monitors. Instead, our hardware boxes and cloud-based services perform real-time, two-way communication over the Internet to determine what power quality data must be gathered and with what fidelity in order to most efficiently produce actionable information. Two-way communication between the OPQ Boxes and cloud services creates the ability to control individual OPQ Boxes based upon the global state of all OPQ Boxes in an OPQ sensor network. As a result, OPQ cloud services can obtain and analyze high fidelity waveform data only when desired, without the prohibitive network overhead of constantly communicating this data from boxes to the cloud. This enables OPQ installations to be simultaneously responsive and scalable.

### 2020-06-24 03-architecture.tex
wave form -> waveform.

OPQ's "information architecture" is designed to facilitate the process of generating actionable, useful insights into the nature of the electrical grid starting with the data collected from a wall outlet. The information architecture must address several requirements. First, it must support analyses that require access to high fidelity data, which in the case of power quality is wave form data produced by sampling the wave form 256 times per cycle (or 12,000 times per second), which means there are approximately 1 billion data points generated per day per OPQ Box. Second, for typical grids that are generally stable, only an extremely small fraction of these data points are actually interesting. Third, as will be discussed in more detail later, what constitutes ``interesting'' data in one box might be dependent upon the state of data in other nearby boxes. Finally, network and storage limitations preclude a solution in which all data is sent from OPQ Boxes to the cloud, and so the information architecture must provide a ``smart'' mechanism for identifying data of interest on the boxes, as well as discarding data in the cloud if it is found to be not useful.

@@

\begin{table}[ht]
\caption{OPQ Information Architecture Levels}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{llp{4in}}
\toprule
\textbf{Layer}	& \textbf{TTL}	& \textbf{Purpose}\\
\midrule
Box		& 1 hour			& Collects and holds a rolling one hour window of "high fidelity" instantaneous wave form data measurements for a single location.\\
Measurement		& 1 day/2 weeks		& Aggregate measurements provide "low fidelity" summary statistics regarding four power measurements (Frequency, Voltage, THD, Transients) at a rate of either 1/second (Measurement) or 1/day (Trend). Measurements and Trends both collect summary statistics, but at different window lengths and with different TTLs.\\
Event/Detection & 1 month & When OPQ Cloud's Makai service detects non-nominal values in the stream of Measurements, it can decide to request an ``event'': wave form data from one or more boxes for a specific time interval (typically, just a second or so). \\
Incident & 6 months & An Incident is generated by OPQ Cloud's Mauka when an Event satisfies a standard (such as IEEE 1159, ITIC, or SEMA) for a significant power quality problem.\\
Phenomena & 1 year & Phenomena classify Incidents when they are predictable and/or have a known causal explanation. \\
\bottomrule
\end{tabular}
\label{fig:information-architecture}
\end{table}

@@

Approximately once a second, each Box sends a Measurement data object to the sensor network's cloud services, which we refer to in aggregate as OPQ Cloud. Measurements are the second layer of the information architecture, and provide "low fidelity" summary statistics regarding four power quality measurements (Frequency, Voltage, THD, and Transients). Measurements give OPQ Cloud basic situational awareness of the grid without the overhead of transmitting, storing, and analyzing high fidelity wave form data. Measurements exist for one day, though a daily roll-up of Measurement summary statistics called "Trends" persists longer.

When OPQ Cloud's Makai service detects non-nominal values in the stream of Measurements, it can decide to request wave form data from one or more boxes for a specific time interval (typically just a second or so). Note that Makai only has one hour to request high fidelity wave form data before it is lost. Mauka may also request Event data for specific Phenomena, which will be discussed in more detail below.

>>>>

OPQ's "information architecture" is designed to facilitate the process of generating actionable, useful insights into the nature of the electrical grid starting with the data collected from a wall outlet. The information architecture must address several requirements. First, it must support analyses that require access to high fidelity data, which in the case of power quality is waveform data produced by sampling the waveform 256 times per cycle (or 12,000 times per second), which means there are approximately 1 billion data points generated per day per OPQ Box. Second, for typical grids that are generally stable, only an extremely small fraction of these data points are actually interesting. Third, as will be discussed in more detail later, what constitutes ``interesting'' data in one box might be dependent upon the state of data in other nearby boxes. Finally, network and storage limitations preclude a solution in which all data is sent from OPQ Boxes to the cloud, and so the information architecture must provide a ``smart'' mechanism for identifying data of interest on the boxes, as well as discarding data in the cloud if it is found to be not useful.

@@

\begin{table}[ht]
\caption{OPQ Information Architecture Levels}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{llp{4in}}
\toprule
\textbf{Layer}	& \textbf{TTL}	& \textbf{Purpose}\\
\midrule
Box		& 1 hour			& Collects and holds a rolling one hour window of "high fidelity" instantaneous waveform data measurements for a single location.\\
Measurement		& 1 day/2 weeks		& Aggregate measurements provide "low fidelity" summary statistics regarding four power measurements (Frequency, Voltage, THD, Transients) at a rate of either 1/second (Measurement) or 1/day (Trend). Measurements and Trends both collect summary statistics, but at different window lengths and with different TTLs.\\
Event/Detection & 1 month & When OPQ Cloud's Makai service detects non-nominal values in the stream of Measurements, it can decide to request an ``event'': waveform data from one or more boxes for a specific time interval (typically, just a second or so). \\
Incident & 6 months & An Incident is generated by OPQ Cloud's Mauka when an Event satisfies a standard (such as IEEE 1159, ITIC, or SEMA) for a significant power quality problem.\\
Phenomena & 1 year & Phenomena classify Incidents when they are predictable and/or have a known causal explanation. \\
\bottomrule
\end{tabular}
\label{fig:information-architecture}
\end{table}

@@

Approximately once a second, each Box sends a Measurement data object to the sensor network's cloud services, which we refer to in aggregate as OPQ Cloud. Measurements are the second layer of the information architecture, and provide "low fidelity" summary statistics regarding four power quality measurements (Frequency, Voltage, THD, and Transients). Measurements give OPQ Cloud basic situational awareness of the grid without the overhead of transmitting, storing, and analyzing high fidelity waveform data. Measurements exist for one day, though a daily roll-up of Measurement summary statistics called "Trends" persists longer.

When OPQ Cloud's Makai service detects non-nominal values in the stream of Measurements, it can decide to request waveform data from one or more boxes for a specific time interval (typically just a second or so). Note that Makai only has one hour to request high fidelity waveform data before it is lost. Mauka may also request Event data for specific Phenomena, which will be discussed in more detail below.

### 2020-06-24 07-opq-mauka.tex
wave form -> waveform.

The lowest layer of the hierarchy is the Instantaneous Measurements Layer (IML). The IML contains "raw" data, in other words, the digitize waveform.  IML data exists both on each OPQ Box (where it is available for up to the previous 60 minutes). It also exists in the cloud, in the event that OPQ's triggering mechanism has caused a temporal interval of waveform data to be uploaded. IML data in the cloud has a TTL of 15 minutes: unless the wave form data is found to be useful by a cloud service within 15 minutes, it can be discarded.

>>>>

The lowest layer of the hierarchy is the Instantaneous Measurements Layer (IML). The IML contains "raw" data, in other words, the digitize waveform.  IML data exists both on each OPQ Box (where it is available for up to the previous 60 minutes). It also exists in the cloud, in the event that OPQ's triggering mechanism has caused a temporal interval of waveform data to be uploaded. IML data in the cloud has a TTL of 15 minutes: unless the waveform data is found to be useful by a cloud service within 15 minutes, it can be discarded.

### 2020-06-24 09-pilot.tex
wave form -> waveform.

One interesting capability enabled by two way communication between OPQ Boxes and their cloud-based services is what we term {\em subthreshold event detection based on temporal locality}.
In a nutshell, when one OPQ Box determines that a power quality measure has exceeded a threshold, one of the actions of the sensor network is to request high fidelity wave form data from neighboring boxes for the same temporal period, regardless of whether those boxes are reporting over-threshold data.
In the event that any of those boxes actually do report over-threshold data, then the request ripples outward to the boxes neighboring that box, and so forth.
This is accomplished by maintaining an model of the OPQ Box metrics for each device.
Once a single device passes a threshold, OPQ Makai will search the network for all other devices which exhibit measurements which deviate significantly from the device model.
If more devices are located, data from all the affected devices will be captured.
Otherwise the event is deemed local and ignored.

>>>>

One interesting capability enabled by two way communication between OPQ Boxes and their cloud-based services is what we term {\em subthreshold event detection based on temporal locality}.
In a nutshell, when one OPQ Box determines that a power quality measure has exceeded a threshold, one of the actions of the sensor network is to request high fidelity waveform data from neighboring boxes for the same temporal period, regardless of whether those boxes are reporting over-threshold data.
In the event that any of those boxes actually do report over-threshold data, then the request ripples outward to the boxes neighboring that box, and so forth.
This is accomplished by maintaining an model of the OPQ Box metrics for each device.
Once a single device passes a threshold, OPQ Makai will search the network for all other devices which exhibit measurements which deviate significantly from the device model.
If more devices are located, data from all the affected devices will be captured.
Otherwise the event is deemed local and ignored.
